Descriptives and model description

### 2022-12-09 descriptives.qmd
update missingness/region plot

### packages
library(tidyverse)
library(stringi)
library(gt)
library(ggplot2)
library(patchwork)

@@

p.oriregion.missingAge1 <- ggplot(data = t.oriregion.missingAge %>%
                                   filter(origin_region!="Oceania", missingAge == "Age not missing") %>% 
                                    pivot_longer(cols = c(children, adults), names_to = "age", values_to = "value"),
                                                 aes(x = origin_region, 
                                                     y = value, 
                                                     fill = age)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values=c(unhcrPaletteBlue[1], unhcrPaletteGreen[1])) +
  ggtitle("Age data available") +
  ylim(c(NA,5000000)) +
  theme(legend.position = "bottom") +
  theme_minimal()

p.oriregion.missingAge2 <- ggplot(data = t.oriregion.missingAge %>%
                                   filter(origin_region!="Oceania", missingAge == "Age missing") ,
                                                 aes(x = origin_region, 
                                                     y = total)) +
  geom_bar(stat = "identity", colour = unhcrPaletteBlue[1], fill = unhcrPaletteWhite[1], alpha = 0)  +
  ggtitle("Age data missing") +
  theme_minimal()

p.oriregion.missingAge1  + p.oriregion.missingAge2+ plot_layout(guides = "collect") & theme(legend.position = "bottom") & ylim(c(NA,11000000))

>>>>

### packages
library(tidyverse)
library(stringi)
library(gt)
library(ggplot2)
library(patchwork)
library(scales)

@@

p.oriregion.missingAge1 <- ggplot(data = t.oriregion.missingAge %>%
                                   filter(origin_region!="Oceania", missingAge == "Age not missing") %>% 
                                    pivot_longer(cols = c(children, adults), names_to = "age", values_to = "value"),
                                                 aes(x = origin_region, 
                                                     y = value, 
                                                     fill = age)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values=c(unhcrPaletteBlue[1], unhcrPaletteGreen[1])) +
  ggtitle("Age data available") +
  labs(y = "Number of refugees")  +
  ylim(c(NA,5000000)) +
  theme(legend.title = element_blank(), legend.position = "bottom") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        panel.grid.major.x = element_blank())

p.oriregion.missingAge2 <- ggplot(data = t.oriregion.missingAge %>%
                                   filter(origin_region!="Oceania", missingAge == "Age missing") ,
                                                 aes(x = origin_region, 
                                                     y = total)) +
  geom_bar(stat = "identity", colour = unhcrPaletteBlue[1], fill = unhcrPaletteWhite[1], alpha = 0,
           size = 1.6)  +
  ggtitle("Age data missing") +
  labs(y = "Number of refugees")  +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        panel.grid.major.x = element_blank()) +
  scale_y_continuous(labels = label_number(scale_cut = cut_si("m")))

p.oriregion.missingAge <- p.oriregion.missingAge1  + p.oriregion.missingAge2+ plot_layout(guides = "collect") & theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size=16))  &  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()), limits = c(NA,11000000))
